### 2013-07-23 doc/asplos14/tasks.tex
pass on tasks

\paragraph{Scheduling} During execution, a worker yields control of its core
whenever performing a long-latency operation, allowing the processor to
remain busy while waiting for the operation to complete. In addition, a
programmer can direct scheduling explicitly.
% via the \Grappa API calls shown in
%Figure~\ref{fig:scheduling}. 
To minimize context-switch overhead, the \Grappa scheduler
operates entirely in user-space and does little more than store state of one
worker and load that of another.
\TODO{mention how we block on response (``scheduler activations'' or whatever) not busy wait}

\TODO{either explain the usage of yield vs suspend in talking about
    short and longer latency tolerance or eliminate the
    distinction}
%% \begin{figure}[htbp]
%%   \begin{center}
%%   \begin{minipage}{0.95\columnwidth}  
%%   \begin{description}
%%     \item[\texttt{yield() }] \hfill \\
%%       Yields core to scheduler, enqueuing caller to be scheduled again soon
%%     \item[\texttt{wake( Worker * $w$ ) }] \hfill \\
%%       Enqueues some other worker $w$ to be scheduled again soon
%%     \item[\texttt{suspend() } ] \hfill \\
%%       Yields core to scheduler, enqueuing caller only once another task calls wake
%% 	\end{description}
%%   \end{minipage}
%%     \begin{minipage}{0.95\columnwidth}
%%       \caption{\label{fig:scheduling} \Grappa scheduling API
%%       \TODO{Drop this? Doesn't seem non-obvious or important.}}
%%     \end{minipage}
%%   \end{center}
%% \end{figure}

@@

\TODO{addressing reviewer2: Grappa provides mechanisms for many
    programming idioms. Also, may parallelism to
    give flexibility to the implementation.}
\Grappa programmers focus on expressing as much parallelism as possible
without concern for where it will execute. \Grappa then chooses where and when
to exploit this parallelism, scheduling as much work as is necessary on each
core to keep it busy in the presence of system latencies and task dependences.

>>>>

\paragraph{Scheduling} During execution, a worker yields control of its core
whenever performing a long-latency operation, allowing the processor to
remain busy while waiting for the operation to complete. In addition, a
programmer can direct scheduling explicitly.
% via the \Grappa API calls shown in
% Figure~\ref{fig:scheduling}. 
To minimize context-switch overhead, the \Grappa scheduler
operates entirely in user-space and does little more than store state of one
worker and load that of another. When a tasks encounters a long-latency operation, its worker is suspended and subsequently woken when the operation completes.

%% Maybe the sentence above is enough for the TODOs below.
%
% \TODO{mention how we block on response (``scheduler activations'' or whatever) not busy wait}
% 
% \TODO{either explain the usage of yield vs suspend in talking about
%     short and longer latency tolerance or eliminate the
%     distinction}

%% \begin{figure}[htbp]
%%   \begin{center}
%%   \begin{minipage}{0.95\columnwidth}  
%%   \begin{description}
%%     \item[\texttt{yield() }] \hfill \\
%%       Yields core to scheduler, enqueuing caller to be scheduled again soon
%%     \item[\texttt{wake( Worker * $w$ ) }] \hfill \\
%%       Enqueues some other worker $w$ to be scheduled again soon
%%     \item[\texttt{suspend() } ] \hfill \\
%%       Yields core to scheduler, enqueuing caller only once another task calls wake
%% 	\end{description}
%%   \end{minipage}
%%     \begin{minipage}{0.95\columnwidth}
%%       \caption{\label{fig:scheduling} \Grappa scheduling API
%%       \TODO{Drop this? Doesn't seem non-obvious or important.}}
%%     \end{minipage}
%%   \end{center}
%% \end{figure}

@@

% \TODO{addressing reviewer2: Grappa provides mechanisms for many
%     programming idioms. Also, may parallelism to
%     give flexibility to the implementation.}

\Grappa programmers focus on expressing as much parallelism as possible
without concern for where it will execute. \Grappa then chooses where and when
to exploit this parallelism, scheduling as much work as is necessary on each
core to keep it busy in the presence of system latencies and task dependences.
